Post-Hurricane Dynamics of Tropical Tree Functional Diversity
=============================================================

Author: [Nate Swenson](http://www.swensonlab.com)

This code generates 50 random numbers from a normal distribution with a mean of zero and a s.d. of 1.

```{r }

rand.vals = rnorm(50)

```

Here we plot a histogram of the 50 random numbers.

```{r }

hist(rand.vals, col="red")

```

Here we are generating 50 random numbers from a normal distribution, but because we set eval=F it does not run the R code and causes downstream calculations to fail.


```{r eval=F}

rand.vals.2 = rnorm(50)

```

Trying to plot a histogram of rand.vals.2

```{r }

hist(rand.vals.2, col="red")

```

Here we make 50 random values and plot them against original 50 random values. Setting figure size to a 2 inch by 3 inch size.

```{r fig.width=2, fig.height=3}

rand.vals.3 = rnorm(50)

plot(rand.vals.3~rand.vals, xlab="First dataset", ylab = "Third dataset", pch=21, bg="orange",cex=2,xlim=c(-5,5),ylim=c(-5,5))
```


Here we make 50 random values and plot them against original 50 random values. Setting figure size to a 5 inch by 5 inch size.

```{r fig.width=5, fig.height=5}

plot(rand.vals.3~rand.vals, xlab="First dataset", ylab = "Third dataset", pch=21, bg="orange",cex=2,xlim=c(-5,5),ylim=c(-5,5))

```
